%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Thin Formal Letter
% LaTeX Template
% Version 2.0 (7/2/17)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Author:
% Vel (vel@LaTeXTemplates.com)
%
% Originally based on an example on WikiBooks
% (http://en.wikibooks.org/wiki/LaTeX/Letters) but rewritten as of v2.0
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
% DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{letter} % 10pt font size default, 11pt and 12pt are also possible

\usepackage{geometry} % Required for adjusting page dimensions

%\longindentation=0pt % Un-commenting this line will push the closing "Sincerely," to the left of the page

\geometry{
  paper=a4paper, % Change to letterpaper for US letter
  top=3cm, % Top margin
  bottom=1.5cm, % Bottom margin
  left=2.5cm, % Left margin
  right=2.5cm, % Right margin
  %showframe, % Uncomment to show how the type block is set on the page
}

\usepackage[T1]{fontenc} % Output font encoding for international characters
\usepackage[utf8]{inputenc} % Required for inputting international characters

\usepackage{stix} % Use the Stix font by default

\usepackage{microtype} % Improve justification
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
%----------------------------------------------------------------------------------------
% YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\signature{Thomas J. Delaney} % Your name for the signature at the bottom

\address{\textbf{Thomas J. Delaney} \\
  81-83 Woodland Road \\
  University of Bristol \\
  Bristol, BS8 1US \\
  United Kingdom \\
  t.delaney@bristol.ac.uk} % Your address and phone number

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
% ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{Undergraduate Scholars Program \\
  HHMI Janelia Research Campus \\
  19700 Helix Drive\\
  Ashburn \\
  Virginia \\
  United States of America} % Name/title of the addressee

%----------------------------------------------------------------------------------------
% LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

  \opening{\textbf{Dear Sir/Madame,}}

  %%%%%%%%%%%%%%% INTRODUCTION %%%%%%%%%%%%%%%%%%%
  I am writing to you to provide a reference for Mr. Mohit Kulkarni, as part of his application to attend the Undergraduate Scholars Program in the Janelia Research Campus. I was the Teaching Assistant in charge of a group of students including Mohit during the Neuromatch Academy in July, 2020. I found Mohit to be a very impressive student.

  Since Mohit is a mathematics undergraduate student, he displayed a good understanding of the mathematics behind the analysis techniques employed during the Neuromatch Academy. However, he also has a great diversity of knowledge and academic interests. He has knowledge of machine learning, time series analysis, reinforcement learning etc., etc. He also had some neuroscience knowledge before the academy and learned quite a lot about computational neuroscience during the academy. He also has expertise in coding in Python. He took on all of the coding work for his group's project at the end of the course. This was no small task. Mohit was also well able to pass on this coding knowledge to the less experienced members of his group. His communication with other members was clear, concise, and always helpful.

  As well as knowledge and understanding, Mohit has a tremendous curiosity about neuroscience, and computational neuroscience particularly. He is always enthusiastic to learn about ideas and techniques that are new to him. In my opinion, this is a vital characteristic for a scientist. I believe that Mohit has huge potential as a scientist.

  On a personal level, Mohit is polite and congenial. He is delightful to work with. He always attended zoom meetings on time, and informed me well in advance if he was not able to attend. If you would like to ask any additional questions, feel free to contact me on (+353) 0861275282, or email me at td16954@bristol.ac.uk.

  \vspace{2\parskip} % Extra whitespace for aesthetics
  \closing{Sincerely,}
  \vspace{2\parskip} % Extra whitespace for aesthetics

%  \ps{P.S. You can find additional information attached to this letter.} % Postscript text, comment this line to remove it

%  \encl{Copyright permission form} % Enclosures with the letter, comment this line to remove it

  %----------------------------------------------------------------------------------------

\end{letter}

\end{document}
