%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Thomas J. Delaney, PhD} % Your name
\address{Ballyboggan Lower \\ Castlebridge} % Your address
\address{Co. Wexford \\ Ireland} % Your secondary addess (optional)
\address{(+353) 0861275282 \\ thomas.delaney@posteo.net} % Your phone number and email (353) 086 127 5282

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf University of Bristol} \hfill {\em Sept 2016 - July 2020} \\
PhD in Computer Science \\
Specialising in computational neuroscience. \\
Thesis: `Investigating, implementing, and creating methods for analysing large neuronal ensembles' \\
Focussed on dynamic modelling of calcium fluoresence, and statistical modelling of activity in neuronal ensembles, \\
Multiple conference presentations, and a work in progress for publication

{\bf University of Edinburgh} \hfill {\em Sept 2014 - Sept 2015} \\
MSc in Informatics \\
Thesis in `How informative are retinal ganglion cell responses about visual stimuli?' \\
Modules included: Neural Computation, Machine Learning \& Pattern Recognition, Reinforcement Learning, Neural Information Processing, etc.  \smallskip \\
Overall Result: Distinction

{\bf Trinity College, Dublin} \hfill {\em Sept 2007 - June 2011} \\
B.A. in Mathematics \\
Including two years of Theoretical Physics \\
Final Year Project on Quantum Topos Theory \\
Poster Project entitled `Biomechanics of Human Motion' \\
Modules included: Mathematical Neuroscience, Introduction to Information Theory, Functional Analysis, etc. \smallskip \\
Overall Result: 1.1

% {\bf St. Peter's College, Wexford} \hfill {\em Sept 2002 - June 2007} \\
% Leaving Certificate - 550 points \\
% A1 results in Maths, Physics, Technical Drawing
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

  \begin{rSubsection}{University of Bristol}{Sept 2016 - Present}{Teaching Assistant}{Bristol, England}
    \item Teaching Assistant for Computer Science and Engineering Mathematics undergraduate and MSc courses:
      \begin{itemize}
        \item[$\circ$] Applied Statistics, $3$rd year \&  MSc course, $2018 - 2020$, $\sim 80$ students.
        \item[$\circ$] Machine Learning, $3$rd year \& MSc course, $2019$, $\sim 300$ students.
        \item[$\circ$] Data Structures \& Algorithms, $2$nd year course, $2019$, $\sim 200$ students.
        \item[$\circ$] Algorithms, $1$st year course, $2018$, $\sim 200$ students.
      \end{itemize}\vspace{1.5mm}
    \item Marking for undergraduate courses:
      \begin{itemize}
        \item[$\circ$] Algorithms, $1$st year course, $2018$, $\sim 200$ students.
        \item[$\circ$] Computational Neuroscience, $3$rd year \& MSc course, $2018-2019$, $\sim 300$ students.
      \end{itemize}\vspace{1.5mm}
    \item Prepared workshop for prospective computer science students on university open day.
  \end{rSubsection}

\newpage

  \begin{rSubsection}{University of Bristol}{January 2017 - Present}{Chief Examination Invigilator}{Bristol, England}
    \item Supervised $\sim 50$ exam rooms.
    \item Includes exam rooms for a single student and for up to $800$ students.
    \item Responsible for set-up, role taking, reportage of malpractice, safe transport of exam scripts and papers.
  \end{rSubsection}

  \begin{rSubsection}{CheckRisk}{June 2018 - September 2018}{Research Internship}{Bath, England}
    \item Internship at financial risk assessment company.
    \item Researched cutting-edge forecasting methods including statistical, machine learning and hybrid methods, including recurrent neural networks.
    \item Applied these methods to financial data to evaluate domain suitability.
  \end{rSubsection}

  \begin{rSubsection}{Edinburgh Airport Ltd.}{Jan 2016 - Aug 2016}{Data Engineer}{Edinburgh, Scotland}
    \item Worked as a key member of the Airport's Digital team with a mandate to change every interaction with the airport using technology, data and innovation.
    \item Main responsibility involved taking in data available from around the business and extracting insights quickly and at low cost.
    \item Worked with teams such as Commercial, Security, Airfield, Forecasting and Planning to extract, transform and load data, making these datasets useful for these teams, and Edinburgh Airport’s senior management.
  \end{rSubsection}

  \begin{rSubsection}{First Derivatives. Plc}{June 2011 - Aug 2014}{Consultant Software Engineer}{Newry, Ireland}
    \item Worked as a software engineer on in-house projects, and as a consultant for different financial companies and institutions.
    \item Four months as kdb+ consultant in Morgan Stanley New York offices, working on the creation and upkeep of a large historical and real-time financial database.
    \item Four months as kdb+ consultant and team leader in off-shore development centre for Morgan Stanley.
    \item Seventeen months as kdb+ consultant in a highly responsible role in the London based hedge fund Marshall Wace Asset Management.
    \item Final three months in team-leader role utilising in-house software for performance reporting on First Derivatives FX trading platform.
  \end{rSubsection}

%------------------------------------------------

  % \begin{rSubsection}{Trinity College Mathematics Dept.}{May 2010 - Aug 2010}{Summer Intern}{Dublin, Ireland}
  %   \item Composed a project entitled `The Historical and Mathematical Development of Maxwell's Equations'.
  %   \item Detailed the development of Maxwell's equations from a scientific and mathematical point of view.
  %   \item Attended weekly meetings with the project supervisor from the Mathematics Dept.
  %   \item Ensured part of this project would be suitable for use in the Classical Field theory or Classical Electrodynamics course in Trinity college.
  % \end{rSubsection}

%------------------------------------------------

%\begin{rSubsection}{Tesco Ireland}{June 2007 - January 2010}{General Assistant}{Wexford, Ireland}
%\item  Kept the shelves well stocked.
%\item  Helped customers with any questions or queries.
%\item  Occasionally worked on the checkout, particularly at
%the busiest times of the week.
%\item  Kept the work environment clean, tidy and safe at all
%times.
%\end{rSubsection}
%
%\begin{rSubsection}{Maxol Mace Service Station Ardcavan}{June 2006 - Sept 2006}{Sales Assistant}{Wexford, Ireland}
%\item  Main responsibility was operating the till.
%\item  Also helped customers with any questions or queries, kept track of the petrol pumps, and kept the environment clean and tidy.
%\end{rSubsection}
%
\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages  & Python, Julia, Matlab, Bash, q/kdb+, Java, c++, Batch Scripting, \\
                    & \LaTeX \\
Protocols \& APIs   & FIX messaging protocol, Geneos monitoring API \\
Databases           & kdb+, MySQL  \\
Tools               & git, SVN, Vim, crontab, Autosys, Eclipse, Scoop for Parallel Processing
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	Scholarship section
%----------------------------------------------------------------------------------------

\begin{rSection}{Scholarships}

Bristol PhD studentship, funded by the EPSRC \\
University of Edinburgh Informatics UK/EU Master's Scholarship 2014/2015 \\
Exempt from Senior Freshman Mathematics Final Exams by virtue of Trinity Foundation Scholarship exam results.

\end{rSection}

%----------------------------------------------------------------------------------------
%	ACHIEVEMENTS
%----------------------------------------------------------------------------------------
% \begin{rSection}{Achievements}
%
% \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
% Academic 		& Consistently excellent academic performance in a number well reputed of \\
% 				& universities. \\
% Professional 	& Working in Morgan Stanley within 3 months of finishing undergraduate degree. \\
% 				& Maintaining a consistently high standard of work in every environment.
% \end{tabular}
%
% \end{rSection}

%----------------------------------------------------------------------------------------
%	Other Interests
%----------------------------------------------------------------------------------------
% \begin{rSection}{Other Interests \& Skills}
%
% \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
% Spoken Languages & English (fluent), Gaeilge (proficient), French (basic) \\
% Sport & Weightlifting, Boxing, GAA (member of University of Edinburgh \\
% & Gaelic Football Team), Soccer \\
% Reading & Sport or Maths related non-fiction, Irish fiction, etc. \\
% Gambling Technology & Using my coding and software knowledge to predict the outcomes of \\
% & games and matches.
% \end{tabular}
%
% \end{rSection}

%----------------------------------------------------------------------------------------
%	References
%----------------------------------------------------------------------------------------
%\begin{rSection}{References}
% Available on request
%\end{rSection}


\end{document}
