%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Thomas Delaney} % Your name
\address{Office 2.03 \\ 81-83 Woodland Road} % Your address
\address{University of Bristol \\ Clifton} % Your address
\address{Bristol, UK \\ BS8 1US} % Your secondary addess (optional)
\address{(+353)0861275282 \\ t.delaney@bristol.ac.uk} % Your phone number and email (353) 086 127 5282

\begin{document}

%----------------------------------------------------------------------------------------
%	RESEARCH INTERESTS
%----------------------------------------------------------------------------------------

\begin{rSection}{Research Interests}
  Statistical modelling of large populations of neurons, particularly in response to stimuli \\
  Statistical hierarchical models of the brain \\
  Information theory in neuroscience \\
  Machine learning models of sensory perception 
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
  \begin{rSubsection}{University of Bristol}{Sept 2016 - Present}{Candidate for PhD, Computer Science}{Bristol, England}
    \item Biophysical modelling of in-vivo fluorescent calcium indicators.
    \item Statistical analysis of the activity of large populations of neurons, comparing functional clustering of neurons with their anatomical distribution.
  \end{rSubsection}
  
  \begin{rSubsection}{Online learning}{Nov 2017 - Feb 2018}{Neural Networks for Machine Learning}{coursera.org}
    \item Course designed by Geoffrey Hinton, University of Toronto 
  \end{rSubsection}

  \begin{rSubsection}{University of Edinburgh}{Sept 2014 - Sept 2015}{MSc Informatics}{Edinburgh, Scotland}
    \item Thesis: How informative are retinal ganglion cell responses about visual stimuli?
    \item Overall Result: Distinction
  \end{rSubsection}

  \begin{rSubsection}{Trinity College Dublin}{Sept 2007 - June 2011}{BA Mathematics}{Dublin, Ireland}
    \item Final Year Project: Quantum Topos Theory 
    \item Overall Result: 1.1
  \end{rSubsection}

%  \begin{rSubsection}{St. Peter's College}{Sept 2002 - June 2007}{Leaving Certificate}{Wexford, Ireland}
%    \item 550 points   
%  \end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
%       Conference presentations
%----------------------------------------------------------------------------------------

\begin{rSection}{Conference presentations}
  \textbf{Neural Coding, Computation, and Dynamics} \hfill Capbreton, France \\ \vspace{1.5mm}
  Poster: Comparing functional clustering to anatomical distribution \hfill \textit{September, 2019} \\
  \textbf{CNS} \hfill Barcelona, Spain \\ \vspace{1.5mm}
  Poster: Comparing functional clustering to anatomical distribution \hfill \textit{July, 2019}\\
  \textbf{UK Neural computation} \hfill Nottingham, England \\ \vspace{1.5mm}
  Poster: Comparing functional clustering to anatomical distribution \hfill \textit{July, 2019}\\
  \textbf{COSYNE} \hfill Denver, CO, USA \\ \vspace{1.5mm}
  Poster: Calcium imaging model \hfill \textit{March, 2018}\\
  \textbf{BNA Festival of Neuroscience} \hfill Birmingham, England \\ \vspace{1.5mm}
  Poster: Calcium imaging model \hfill \textit{April, 2017}
\end{rSection}

\newpage

%----------------------------------------------------------------------------------------
%       RESEARCH INTERESTS
%----------------------------------------------------------------------------------------
% \begin{rSection}
%   \begin{rSubsection}{Statistical modelling of large populations of neurons}
%     \item Interested in creating models useful for anaylsing the activity of large numbers of neurons. Particularly built on data from up-to-date electrophysiological methods.
%   \end{rSubsection}
% \end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Professional Experience}

  \begin{rSubsection}{University of Bristol}{Sept 2016 - Present}{Teaching Assistant/Invigilator}{Bristol, England}
    \item Teaching Assistant for a variety of courses, Applied Statistics, Data Structures \& Algorithms, Machine Learning, Computational Neuroscience, etc.
    \item Marking for Data Structures \& Algorithms, Computational Neuroscience.
    \item Prepared workshop for prospective computer science students on university open day.
    \item Invigilated examinations.
  \end{rSubsection}

  \begin{rSubsection}{CheckRisk}{June 2018 - September 2018}{Research Internship}{Bath, England}
    \item Internship at financial risk assessment company. 
    \item Researched cutting-edge forecasting methods including statistical, machine learning and hybrid methods, including recurrent neural networks. 
    \item Applied these methods to financial data to evaluate domain suitability.
  \end{rSubsection}

  \begin{rSubsection}{Edinburgh Airport Ltd.}{Jan 2016 - Aug 2016}{Data Engineer}{Edinburgh, Scotland}
    \item Worked as a key member of the Airport's Digital team with a mandate to change every interaction with the airport using technology, data and innovation.
    \item Main responsibility involved taking in data available from around the business and extracting insights quickly and at low cost.
    \item Worked with teams such as Commercial, Security, Airfield, Forecasting and Planning to extract, transform and load data, making these datasets useful for these teams, and Edinburgh Airport’s senior management.
  \end{rSubsection}

  \begin{rSubsection}{First Derivatives. Plc}{June 2011 - Aug 2014}{Consultant Software Engineer}{Newry, Ireland}
    \item Worked as a software engineer on in-house projects, and as a consultant for different financial companies and institutions.
    \item Four months as kdb+ consultant in Morgan Stanley New York offices, working on the creation and upkeep of a large historical and real-time financial database.
    \item Four months as kdb+ consultant and team leader in off-shore development centre for Morgan Stanley.
    \item Seventeen months as kdb+ consultant in a highly responsible role in the London based hedge fund Marshall Wace Asset Management.
    \item Final three months in team-leader role utilising in-house software for performance reporting on First Derivatives FX trading platform.
  \end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Trinity College Mathematics Dept.}{May 2010 - Aug 2010}{Summer Intern}{Dublin, Ireland}
\item Composed a project entitled `The Historical and Mathematical Development of Maxwell's Equations'.
\item Detailed the development of Maxwell's equations from a scientific and mathematical point of view.
\item Attended weekly meetings with the project supervisor from the Mathematics Dept.
\item Ensured part of this project would be suitable for use in the Classical Field theory or Classical Electrodynamics course in Trinity college.

\end{rSubsection}

\newpage

%----------------------------------------------------------------------------------------
%	Scholarship section
%----------------------------------------------------------------------------------------

\begin{rSection}{Scholarships \& Awards}

Bristol PhD studentship, funded by the EPSRC \\
University of Edinburgh Informatics UK/EU Master's Scholarship 2014/2015 \\
Exemption from Senior Freshman Mathematics Final Exams, Trinity Foundation Scholarship exam results.

\end{rSection}

%------------------------------------------------

%\begin{rSubsection}{Tesco Ireland}{June 2007 - January 2010}{General Assistant}{Wexford, Ireland}
%\item  Kept the shelves well stocked.
%\item  Helped customers with any questions or queries.
%\item  Occasionally worked on the checkout, particularly at
%the busiest times of the week.
%\item  Kept the work environment clean, tidy and safe at all
%times.
%\end{rSubsection}
%
%\begin{rSubsection}{Maxol Mace Service Station Ardcavan}{June 2006 - Sept 2006}{Sales Assistant}{Wexford, Ireland}
%\item  Main responsibility was operating the till.
%\item  Also helped customers with any questions or queries, kept track of the petrol pumps, and kept the environment clean and tidy.
%\end{rSubsection}
%
\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages  & Python, Julia, Matlab, Bash, q/kdb+, Java, c++, Batch Scripting, \\ 
                    & \LaTeX \\
Protocols \& APIs   & FIX messaging protocol, Geneos monitoring API \\
Databases           & kdb+, MySQL  \\
Tools               & git, SVN, Vim, crontab, Autosys, Eclipse, Scoop for Parallel Processing
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	ACHIEVEMENTS
%----------------------------------------------------------------------------------------
\begin{rSection}{Achievements}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Academic 		& Consistently excellent academic performance in a number well reputed of \\
				& universities. \\
Professional 	& Working in Morgan Stanley within 3 months of finishing undergraduate degree. \\
				& Maintaining a consistently high standard of work in every environment.
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	Other Interests
%----------------------------------------------------------------------------------------
\begin{rSection}{Other Interests \& Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Spoken Languages & English (fluent), Gaeilge (proficient), French (basic) \\
Sport & Weightlifting, Boxing, GAA (member of University of Edinburgh \\
& Gaelic Football Team), Soccer \\
Reading & Sport or Maths related non-fiction, Irish fiction, etc. \\
Gambling Technology & Using my coding and software knowledge to predict the outcomes of \\
& games and matches.
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	References
%----------------------------------------------------------------------------------------
%\begin{rSection}{References}
% Available on request
%\end{rSection}


\end{document}
